---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# deploytidymodels

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/tidymodelsdeploy)](https://CRAN.R-project.org/package=tidymodelsdeploy)
<!-- badges: end -->

The goal of deploytidymodels is to provide fluent tooling to version, share, and deploy a trained model [workflow](https://workflows.tidymodels.org/). Functions handle both recording and checking the model's input data prototype, and loading the packages needed for prediction.

## Installation

~~You can install the released version of deploytidymodels from [CRAN](https://CRAN.R-project.org) with:~~

``` r
install.packages("deploytidymodels") ## not yet
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("juliasilge/deploytidymodels")
```

## Example

You can use the [tidymodels](https://www.tidymodels.org/) ecosystem to train a model, with a wide variety of preprocessing and model estimation options.

```{r}
library(parsnip)
library(workflows)
data(Sacramento, package = "modeldata")

rf_spec <-
    rand_forest() %>%
    set_mode("regression") %>%
    set_engine("ranger")

rf_fit <-
    workflow() %>%
    add_formula(price ~ type + sqft + beds + baths) %>%
    add_model(rf_spec) %>%
    fit(Sacramento)

rf_fit
```

You can **version** and **share** your model by [pinning](https://pins.rstudio.com/dev/) it, to a local folder, RStudio Connect, Amazon S3, and more.

```{r}
library(deploytidymodels)
library(pins)
library(plumber)

model_board <- board_temp()
model_board %>% pin_model(rf_fit, model_id = "sacramento_rf")
```

You can **deploy** your pinned model via a [Plumber API](https://www.rplumber.io/), which can be [hosted in a variety of ways](https://www.rplumber.io/articles/hosting.html).

```{r, eval=FALSE}
pr() %>%
    pr_model(model_board, "sacramento_rf") %>%
    pr_run(port = 8088)
```

Make predictions with your deployed model at its endpoint and new data.

```{r eval=FALSE}
library(tidyverse)
library(deploytidymodels)
data(Sacramento, package = "modeldata")

new_sac <- Sacramento %>% 
    slice_sample(n = 20) %>% 
    select(type, sqft, beds, baths)

predict_api("http://127.0.0.1:8088/predict", new_sac)
```


## Contributing

This project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

- For questions and discussions about tidymodels packages, modeling, and machine learning, please [post on RStudio Community](https://community.rstudio.com/new-topic?category_id=15&tags=tidymodels,question).

- If you think you have encountered a bug, please [submit an issue](https://github.com/tidymodels/deploytidymodels/issues).

- Either way, learn how to create and share a [reprex](https://reprex.tidyverse.org/articles/articles/learn-reprex.html) (a minimal, reproducible example), to clearly communicate about your code.

- Check out further details on [contributing guidelines for tidymodels packages](https://www.tidymodels.org/contribute/) and [how to get help](https://www.tidymodels.org/help/).
